Optimal (Multiway) Spatial Joins

### 2024-05-29 4.2.tex
4.2

First, we prove (1). By the definition of $\dcross_H(\bm{t})$ and $\dcross_V(\bm{t})$, $h$ and $v$ crosses $B_\bm{t}$. Thus, the intersection of $h$ and $v$ is a point in $B_\bm{t}$. Since $B_\bm{t}$ is the intersection of $\bm{t}[1],...,\bm{t}[k-2]$, the intersection of $h$ and $v$ lies in all the rectangles $r_1,...,r_{k-2}$. Therefore, $h\cap v\bigcap_{i = 1}^{k-2}r_i \neq \emptyset$, and  the tuple $(r_1,...,r_{k-2},h,v)$ is a result tuple in $\J(R_1,...,R_{k-2},H,V)$.

Next, we prove (2). Since $(r_1,...,r_{k-2},h,v)\in \J_1$, both $h$
 and $v$ cross the rectangles $r_1,...,r_{k-2}$ which means that for $i\in[k-2]$, the y-coorninate of $h$ is in the range $[\ybot(r_i'), \ytop(r_i')]$ and the x-coordinate of $v$ is in $[\xleft(r_i'), \xright(r_i')]$. Additionally, for each $i\in[k-2]$, the x-range (resp. y-range) of $r_i'$ is a subset of the x-range (resp. y-range) of $r_i$, so $h$ (resp. $v$) crosses the rectangles $r_i'$. Hence, the point $h \cap v$ is in $B_\bm{t}$, and $h \cap v$ crosses $B_{\bm{t}}$. The former implies that $\bm{t} \in \J(R_1',...,R_{k-2}')$, and the latter implies that $h \in \dcross_H(\bm{t})$ and $v \in \dcross_V(\bm{t})$.

>>>>

First, we prove (1). By the definition of $\dcross_H(\bm{t})$ and $\dcross_V(\bm{t})$, $h$ and $v$ cross $B_\bm{t}$. Thus, the intersection of $h$ and $v$ is a point in $B_\bm{t}$. Since $B_\bm{t}$ is the intersection of $\bm{t}[1],...,\bm{t}[k-2]$, the intersection of $h$ and $v$ lies in all the rectangles $r_1,...,r_{k-2}$. Therefore, $h\cap v\bigcap_{i = 1}^{k-2}r_i \neq \emptyset$, and  the tuple $(r_1,...,r_{k-2},h,v)$ is a result tuple in $\J(R_1,...,R_{k-2},H,V)$.

Next, we prove (2). Since $(r_1,...,r_{k-2},h,v)\in \J_1$, both $h$
 and $v$ cross the rectangles $r_1,...,r_{k-2}$ which means that for $i\in[k-2]$, the y-coorninate of $h$ is in the range $[\ybot(r_i'), \ytop(r_i')]$ and the x-coordinate of $v$ is in $[\xleft(r_i'), \xright(r_i')]$. Additionally, for each $i\in[k-2]$, the x-range (resp. y-range) of $r_i'$ is a subset of the x-range (resp. y-range) of $r_i$, so $h$ (resp. $v$) crosses the rectangles $r_i'$. Hence, the point $h \cap v$ is in $B_\bm{t}$, and $h, v$ cross $B_{\bm{t}}$. The former implies that $\bm{t} \in \J(R_1',...,R_{k-2}')$, and the latter implies that $h \in \dcross_H(\bm{t})$ and $v \in \dcross_V(\bm{t})$.
